Hardware accelerator coupling in heterogeneous systems: an evaluation in the security domain

### 2019-12-10 reports/presentation.tex
write more

\begin{frame}{Experimental setup}
  \begin{minipage}[0.2\textheight]{\textwidth}
    \begin{columns}[T]
      \begin{column}{0.8\textwidth}
        \begin{itemize}
        \item Three Simon accelerators
        \begin{itemize}
        \item MMIO (loosely-coupled)
        \item RoCC (tightly-coupled)
        \item RoCC + DMA (hybrid)
          \end{itemize}
        \end{itemize}
      \end{column}
      \begin{column}{0.2\textwidth}
        \includegraphics[width=2.5cm]{media/cogs.jpeg}
      \end{column}
    \end{columns}
  \end{minipage}
  \begin{itemize}
  \item Both in-order (Rocket) and out-of-order (BOOM) cores
  \item Performance: eight benchmarks run on cycle-accurate simulations
    \begin{itemize}
    \item Software only: ECB and CBC mode
    \item MMIO accelerator, single: ECB and CBC mode
    \item MMIO accelerator, automatic: ECB mode
    \item Tightly-coupled accelerator: ECB and CBC mode
    \item Hybrid accelerator: ECB mode
    \end{itemize}
  \item Area \& power: HWACC synthesized for Xilinx FPGA, post-implementation
    metrics extracted
  \end{itemize}
\end{frame}

@@

\begin{frame}{Results: area \& power}
\end{frame}

@@

\begin{frame}{Future work}
\end{frame}

>>>>

\begin{frame}{Experimental setup}
  \begin{minipage}[0.2\textheight]{\textwidth}
    \begin{columns}[T]
      \begin{column}{0.8\textwidth}
        \begin{itemize}
        \item Three Simon accelerators
        \begin{itemize}
        \item MMIO (loosely-coupled)
        \item RoCC (tightly-coupled)
        \item RoCC + DMA (hybrid)
          \end{itemize}
        \end{itemize}
      \end{column}
      \begin{column}{0.2\textwidth}
        \includegraphics[width=2.5cm]{media/cogs.jpeg}
      \end{column}
    \end{columns}
  \end{minipage}
  \begin{itemize}
  \item Both in-order (Rocket) and out-of-order (BOOM) cores
  \item SoC built with UC Berkeley's Chipyard (HWACCs attached)
  \item Performance: eight benchmarks run on SoC cycle-accurate simulations
    \begin{itemize}
    \item Software only: ECB and CBC mode
    \item MMIO accelerator, single: ECB and CBC mode
    \item MMIO accelerator, automatic: ECB mode
    \item Tightly-coupled accelerator: ECB and CBC mode
    \item Hybrid accelerator: ECB mode
    \end{itemize}
  \item Area \& power: HWACC synthesized for Xilinx FPGA, post-implementation
    metrics extracted
  \end{itemize}
\end{frame}

@@

\begin{frame}{Results: area \& power}
  \begin{itemize}
  \item Arty FPGA with 20800 LUTs / 41600 FFs available
  \item Usage reports 3119 LUTs and 2004 FFs, $\approx$ 17\% and 19.5\% of the
    total design (SoC) size
  \item Somewhat large usage due to unoptimized key expansion function
  \item ACC power consumption estimated at 8mW, $\approx$ 3\% of total SoC
    estimated power consumption (252mW)
  \item Key expansion function also accounts for most of power consumption at
    $\approx$ 87.5\% of ACC consumption
  \end{itemize}
\end{frame}

@@

\begin{frame}{Future work}
  \begin{itemize}
  \item More flexible accelerators, multiple encryption modes, parallelized decryption
  \item Fully custom HWACC interface \& instructions, not RoCC
  \item Privileged HWACC access, OS support (multi-context)
  \end{itemize}
\end{frame}
